## Original Distribution

The standard deviation associated with 1 probable error is the quantile such that
$\Pr(\sigma < X < \sigma) = 0.5$.
```{r}
sigma <- 1 / qnorm(0.75)
sigma
```


## Functions

Dice 1 values:
```{r}
dice1_values <- function(sd = 1) {
  p <- seq(0.5, 1, length.out = 25)
  m <- 0.5 * (p[-1] + p[-length(p)])
  m <- qnorm(m, mean = 0, sd = 1)
  m[22:24] <- NA_real_
  m
}
```

Dice 2 values: Midpoints of the 24 quantiles from $22 / 25$ to 1.
```{r}
dice2_values <- function(sd = 1) {
  p <- 0.5 + 0.5 * seq(22 / 25, 1, length.out = 25)
  m <- 0.5 * (p[-1] + p[-length(p)])  
  m <- m[!is.na(m)]
  qnorm(m, mean = 0, sd = 1)
}
```

Dice I values:
```{r}
matrix(round(dice1_values(sigma), 2), 6, 4)
```


Dice II values:
```{r}
matrix(round(dice2_values(sigma), 2), 6, 4)
```


## Standard Normal Distribution

Midpoints of the first 24 segments:
```{r}
matrix(round(dice1_values(), 2), 6, 4)
```

Midpoints for the last three points:
```{r}
matrix(round(dice2_values(), 2), 6, 4)
```


## References

- Galton, Francis. 1890. "Dice for Statistical Experiments." *Nature*. May 1, 1890. p. 13--14.
- Stigler, Stephen M. 2002. *Statistics on the Table: The History of Statistical Concepts and Methods.* Harvard UP.
